How predictable is extinction?

### 2018-10-26 doc/gsa2018_talk.tex
redoing auc aspects of in-sample comparisons

\begin{frame}
  \frametitle{Measuring performance: Reciever Operating Characteristic}

@@

\begin{frame}
  \frametitle{Measuring performance: Reciever Operating Characteristic}

@@

\begin{frame}
  \frametitle{\textit{k}-fold cross-validation}

@@

\begin{frame}
  \frametitle{Next steps}

  \begin{itemize}
    \item Consider non-linear/threshold effects of covariates (e.g. GAMM, etc.).
    \item What are the possible effects of other, unconsidered covariates (e.g. foram ecology)?
  \end{itemize}

@@

  \begin{itemize}
    \item \alert{The past matters.} Our best supported model includes our historical covariates and allows all effects to vary over time.
    \item 
  \end{itemize}

>>>>

\begin{frame}
  \frametitle{Measuring performance: confusion matrix}

@@

\begin{frame}
  \frametitle{Measuring performance: Receiver Operating Characteristic}

@@

\begin{frame}
  \frametitle{Measuring performance: \textit{k}-fold cross-validation}

@@

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item None of our models are good at predicting extinction.
      \end{itemize}
    \item<2-> Mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}
